Counterexample-guided Synthesis \\ of Closed-loop Digital Control Systems

### 2016-09-28 paper/paper.tex
Added new reference

Modern implementations of embedded control have proliferated with the availability of low cost devices that can perform simple tasks for linear control, spanning many areas such as environmental control and robotic manipulations. The downside to this approach is that in order to achieve low prices, devices are often limited in their capabilities, be it a low number of gates in an FPGA or short word lengths for microcontrollers. The ubiquity of these devices requires that they have a robust design that ensures the correct behaviour in a number of environments.
For this reason it is necessary to provide design tools that formally verify the correctness of the digital controller and in particular we explore the automatic synthesis of these controllers which reduces the deveopment cost and design time for a number of models.

@@

To the authors' knowledge, there is no existing work on the automatic
synthesis of digital controllers considering FWL effects.  Parameter
synthesis tools such as~\cite{cimatti2013parameter} use bounded model
checking and fixed point computations to find parameters based on user
defined specifications, but they often operate in the continuous domain and
are ill-suited for robust analysis since they have no direct means of
evaluating robustness.  Other tools such as~\cite{economakos2016automated}
are directly aimed at robust stability problems but fail to explore the
effects of FWL in their implementation.  In order to provide a correct by
design controller, \cite{alur2016compositional} requires a user-defined
finite state abstraction to synthesise a digital controller based on high
level specifications.  Whilst this approach directly overcomes the
challenges presented by the FWL problem, it still requires error-prone user
intervention.  A different solution that looks at the other end of the scale
is an approach that synthesises word lengths for know problems as developed
in \cite{jha2013swati}, however this provides neither an optimal word
synthesis nor a comprehensive solution for the problem.  It is from this
vacuum that we seek to explore a CEGIS approach to FWL controller synthesis.

@@

In recent years the development of program synthesis has found many ways to
obtain correct by design programs from high level specifiactions.  One such
approach~\cite{itzhaky2010simple} looks to inductively synthesise invariants
to generate the desired programs.  Since these digital programs are already
constrained by designed to factors such as FWL, these approaches are ideal
for the synthesis of parametric controllers. 
In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS for the
synthesis of switching controllers for stabilizing continuous-time plants
with polynomial dynamics.  The work extends to its application on affine
systems, finding its major challenge in the hardness of solving linear
arithmetic on present SMT solvers.  Since this approach uses switching
states instead of linear dynamics in the digital controller, it entirely
circumvents the FWL problem.  It is also not suitable for the kind of
control we seek to synthesise.  What is needed in this regard is the
combination of a synthesis engine with a control verification tool that
addresses the challenges presented here in the form of FWL effects and
stability measures for LTI SISO controllers.  We take the former
from~\cite{} and the latter from \cite{daes20161} whilst enhancing the
procedure by evaluating the quantaization effects of the Hardware interfaces
(ADC/DAC) to obtain an accurate discrete time FWL representation of the
continuous dynamics.

>>>>

Modern implementations of embedded control have proliferated with the availability of low cost devices that can perform simple tasks for linear control, spanning many areas such as environmental control and robotic manipulations. The downside to this approach is that in order to achieve low prices, devices are often limited in their capabilities, be it a low number of gates in an FPGA or short word lengths for microcontrollers. In most cases a floating point implementation is not feasible and the system can benefit from the added resolution of a fixed point representation. The ubiquity of these devices requires that they have a robust design that ensures the correct behaviour in a number of environments.
For this reason it is necessary to provide design tools that formally verify the correctness of the digital controller and in particular we explore the automatic synthesis of these controllers which reduces the deveopment cost and design time for a number of models.

@@

To the authors' knowledge, there is no existing work on the automatic
synthesis of fixed point digital controllers considering FWL effects.  Parameter
synthesis tools such as~\cite{cimatti2013parameter} use bounded model
checking and fixed point computations to find parameters based on user
defined specifications, but they often operate in the continuous domain and
are ill-suited for robust analysis since they have no direct means of
evaluating robustness.  Other tools such as~\cite{economakos2016automated}
are directly aimed at robust stability problems but fail to explore the
effects of FWL in their implementation.  In order to provide a correct by
design controller, \cite{alur2016compositional} requires a user-defined
finite state abstraction to synthesise a digital controller based on high
level specifications.  Whilst this approach directly overcomes the
challenges presented by the FWL problem, it still requires error-prone user
intervention.  A different solution that looks at the other end of the scale
is an approach that synthesises word lengths for know problems as developed
in \cite{jha2013swati}, however this provides neither an optimal word
synthesis nor a comprehensive solution for the problem.  It is from this
vacuum that we seek to explore a CEGIS approach to FWL controller synthesis.

@@

In recent years the development of program synthesis has found many ways to
obtain correct by design programs from high level specifiactions.  One such
approach~\cite{itzhaky2010simple} looks to inductively synthesise invariants
to generate the desired programs.  Since these digital programs are already
constrained by designed to factors such as FWL, these approaches are ideal
for the synthesis of parametric controllers. 
In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS for the
synthesis of switching controllers for stabilizing continuous-time plants
with polynomial dynamics.  The work extends to its application on affine
systems, finding its major challenge in the hardness of solving linear
arithmetic on present SMT solvers.  Since this approach uses switching
states instead of linear dynamics in the digital controller, it entirely
circumvents the FWL problem.  It is also not suitable for the kind of
control we seek to synthesise.  What is needed in this regard is the
combination of a synthesis engine with a control verification tool that
addresses the challenges presented here in the form of FWL effects and
stability measures for LTI SISO controllers.  We take the former
from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from \cite{daes20161} whilst enhancing the
procedure by evaluating the quantaization effects of the Hardware interfaces
(ADC/DAC) to obtain an accurate discrete time FWL representation of the
continuous dynamics.
